A Tutorial on Tailored Simulation-Based Power Analysis for Experimental Designs with Generalized Linear Mixed Models

### 2023-09-18 docs/manuscript.tex
last edits for preprint publication

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{power analysis, data simulation, sample size, generalized linear mixed model\newline\indent Word count: 7598}
\usepackage{lineno}

@@

This research was funded by a grant from the Volkswagen Foundation (Grant No.~98525).
All R code in this manuscript is available in the project's repository on the Open Science Framework (OSF): \url{https://osf.io/dhwf4/}

@@

In this section, we outline the steps for performing data simulation and a priori power analysis for GLMMs using a case study based on a specific experimental study design from the area of human-AI (artificial intelligence) interaction research. The corresponding code in this manuscript is available in the project's repository on the Open Science Framework (\url{https://osf.io/dhwf4/}).

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{power analysis, data simulation, sample size, generalized linear mixed model\newline\indent Word count: 7600}
\usepackage{lineno}

@@

This research was funded by a grant from the Volkswagen Foundation (Grant No.~98525).
All materials (reproducible manuscript incl.~R code, simulation results) are available in the project's repository on the Open Science Framework (OSF): \url{https://osf.io/dhwf4/}

@@

In this section, we outline the steps for performing data simulation and a priori power analysis for GLMMs using a case study based on a specific experimental study design from the area of human-AI (artificial intelligence) interaction research. All code in this manuscript and simulation results are available in the project's repository on the Open Science Framework (\url{https://osf.io/dhwf4/}).
